On the propriety of restricted Boltzmann machines

### 2016-12-04 writing/appendix/appendix-center.Rmd
Submission

---
title: "Supplementary Material to:  On the propriety of restricted Boltzmann machines"
author: "Andee Kaplan, Daniel Nordman, and Stephen Vardeman"
date: "November, 2016"
linestretch: 2 
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
    number_sections: yes
---

>>>>

---
title: "Supplementary material to:  On the propriety of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Industrial Manufacturing 
      | Systems Engineering Department
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
    number_sections: yes
    template: ../latex/technometrics_article.tex
fontsize: 12pt
blind: true
---

### 2016-12-04 writing/draft.Rmd
Submission

---
title: "On the propriety of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: Department of Statistics
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: latex/header.tex
    number_sections: yes
    template: latex/technometrics_article.tex
fontsize: 12pt
bibliography: references/refs.bib
abstract: |
  A restricted Boltzmann machine (RBM) is an undirected graphical model constructed for discrete or continuous random variables, with two layers, one hidden and one visible, and no conditional dependency within a layer. In recent years, RBMs have risen to prominence due to their connection to deep learning. By treating a hidden layer of one RBM as the visible layer in a second RBM, a deep architecture can be created. RBMs are thought to thereby have the ability to encode very complex and rich structures in data, making them attractive for supervised learning. However, the generative behavior of RBMs is largely unexplored. In this paper, we discuss the relationship between RBM parameter specification in the binary case and the tendency to undesirable model properties such as degeneracy, instability and uninterpretability. We also describe the difficulties that arise in likelihood-based and Bayes fitting of such (highly flexible) models, especially as Gibbs sampling (quasi-Bayes) methods are often advocated for the RBM model structure.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---

>>>>

---
title: "On the propriety of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Department of Industrial and
      | Manufacturing Systems Engineering
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    includes:
      in_header: latex/header.tex
    number_sections: yes
    template: latex/technometrics_article.tex
fontsize: 12pt
bibliography: references/refs.bib
abstract: |
  A restricted Boltzmann machine (RBM) is an undirected graphical model constructed for discrete or continuous random variables, with two layers, one hidden and one visible, and no conditional dependency within a layer. In recent years, RBMs have risen to prominence due to their connection to deep learning. By treating a hidden layer of one RBM as the visible layer in a second RBM, a deep architecture can be created. RBMs are thought to thereby have the ability to encode very complex and rich structures in data, making them attractive for supervised learning. However, the generative behavior of RBMs is largely unexplored. In this paper, we discuss the relationship between RBM parameter specification in the binary case and the tendency to undesirable model properties such as degeneracy, instability and uninterpretability. We also describe the difficulties that arise in likelihood-based and Bayes fitting of such (highly flexible) models, especially as Gibbs sampling (quasi-Bayes) methods are often advocated for the RBM model structure.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---
